\cvsection{Work and Volunteer Experience}

\begin{cventries}
 \cventry
    {International English Language Testing System Teacher} % Job title
    {Global Education \& Technology Co., Ltd.} % Organization
    {Kunming, China} % Location
    {Apr-Sep 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Helped students to achieve ideal test scores which can be used to apply universities overseas.}
        \item{Consistently received positive teacher evaluations from students.}
        \item{Set up lesson materials, bulletin board displays and demonstrations.}
      \end{cvitems}
    }
    
    
  \cventry
    {Marketing Specialist} % Job title
    {Hua Xia Bank} % Organization
    {Kunming, China} % Location
    {Apr-Sep 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed campaigns and specific marketing strategies for clients.}
        \item{Coordinated and participated in promotional activities and trade shows.}
        \item{Consulted with buying personnel to determine projected demand for products and services.}
      \end{cvitems}
    }
    
   
    
    \cventry
    {Accessibility Shuttle Bus Driver} % Job title
    {Congress 2019} % Organization
    {Vancouver, British Columbia} % Location
    {June 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Congress is Canada's largest gathering of scholars for social sciences and humanities.}
        \item {Volunteered as an accessibility shuttle bus driver and received positive feedback from volunteer coordinator. }
      \end{cvitems}
    }
    
    

 
\end{cventries}
