\cvsection{Personal Projects}

\begin{cventries}
  \cventry
    {} % Empty position
    {Tribute Page} % Project
    {} % Empty location
    {July 2019} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
      	\item {Built an introduction page in HTML and CSS for the famous Chinese scientist Yuan Longping who saved millions of lives from hunger.}
		\item {Applied HTML's heading elements to show the hierarchical relationships of the content.  }
      \end{cvitems}
    }

    

  \cventry
    {} % Empty position
    {Survey Form} % Project
    {} % Empty location
    {July 2019} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
      	\item {Built a web page to conduct survey about software developers' technical background. }
		\item {Applied various input fields such as radio buttons, check boxes, drop-down selections to collect information.}
      \end{cvitems}
    }
    
    \cventry
    {} % Empty position
    {Product Landing Webpage} % Project
    {} % Empty location
    {August 2019} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
      	\item {Developed a webpage in HTML and CSS to show the information for
      	BMW's upcoming vehicle, M140i, including specs, prices, pages and professional video review from YouTube. }
		\item {Constructed responsive and flexible page layout by applying CSS media queries and flex box.}
		\item{Included a navigation bar at the top of the page to quickly access to the corresponding sections.}
		\item{Used media queries to verify that the webpage can be viewed correctly on various devices.}
      \end{cvitems}
    }
    
    \cventry
    {} % Empty position
    {Personal Portfolio Webpage} % Project
    {} % Empty location
    {Sep 2019-Present} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
      	\item {Developing a webpage in HTML and CSS to highlight my both academic and personal projects linking to my CodePen or Github.}
		\item {Applying accessibility features to help users rely on assistive technology such as screen reader or voice recognition software.}
      \end{cvitems}
    }
    
    
    
    
    
\end{cventries}